Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-05 doc/main_jfm.tex
updates

\begin{figure}
\centering
\includegraphics[height=2in]{relax.eps}
\includegraphics[height=2in]{relax2.eps}\\
\includegraphics[height=2.in]{N58_0pres.pdf}
\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
  \caption{Vesicle relaxes under a quiescent flow. (a) The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively. The red curve shows the decreasing trend of the mean magnitude of particle orientation change. The black dashed line shows the reference of how all magnitudes decay. (b) Bilayer configurations for $t=0$(gray) and $t=1000$(red) with particle directors.
  }
    \label{figure2}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[height=2in]{relax.eps}
\includegraphics[height=2in]{relax2.eps}\\
\includegraphics[height=2.in]{N58_0pres.pdf}
\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
  \caption{Vesicle relaxes under a quiescent flow. (a) The blue dashed and solid curves are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively. The red curve shows the decreasing trend of the mean magnitude of particle orientation change. The black dashed line shows the reference of how all magnitudes decay. (b) Bilayer configurations for $t=0$(gray) and $t=1000$(red) with particle directors.
  (c)-(d) show the fluid pressure profiles for $t=0$ and $t=1000$ where the background curves indicate the streamlines. In panel (c), the pressure value in internal fluid is much higher than the pressure outside of the bilayer. After the relaxation, this immersed permeable bilayer approaches a steady state as shown in panel (d).
  }
    \label{figure2}
\end{figure}
